Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-26 snapshot_system/fast14_evaluation.tex

% \begin{table*}[t]
%     \centering
%     \begin{tabular}{c|ccc|ccc}
%     Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
%     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
%     per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
%     1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
%     2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
%     4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
%     6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
%     \end{tabular}
% \caption{Throughput of software layers under different concurrency}
% \label{tab:throughput}
% \end{table*}
\begin{table}[htbp]
    \centering
    \begin{tabular}{c|ccc}
    Num. of concurrent      & \multicolumn{3}{c}{Throughput without}    \\
    backup tasks            & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-4}
    per node                & Raw                                        & Snapshot Store & QFS  \\ \hline
    1                       & 1369.6                                     & 148.0          & 18.0 \\
    2                       & 2408.5                                     & 260.2          & 31.7 \\
    4                       & 4101.8                                     & 443.3          & 54.1 \\
    6                       & 5456.5                                     & 589.7          & 72.0 \\
    \end{tabular}
\caption{Throughput of software layers under different concurrency}
\label{tab:throughput}
\end{table}

{\bf Throughput of software layers.}
Table~\ref{tab:throughput} shows the  average throughput of software layer
when I/O is throttled under 50MB/second and when there is no restriction.
%machine when all machine nodes execute one or multiple MV backup tasks.
``Raw'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the gap between this
column and  ``Raw" column is caused by significant data reduction by dirty bit and duplicate
detection. Only non-duplicate chunks trigger a snapshot store write.
``QFS'' column is the write request traffic to the underlying file system after compression.
The underlying disk storage traffic will be three times greater because of replication.
The result shows that the backup service can deliver up to 5.46GB/second without I/O restriction
per machine with 6 concurrent backup tasks. With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

>>>>

% \begin{table*}[t]
%     \centering
%     \begin{tabular}{c|ccc|ccc}
%     Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
%     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
%     per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
%     1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
%     2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
%     4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
%     6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
%     \end{tabular}
% \caption{Throughput of software layers under different concurrency}
% \label{tab:throughput}
% \end{table*}
\begin{table}[htbp]
    \centering
    \begin{tabular}{c|ccc}
    Num. of concurrent      & \multicolumn{3}{c}{Throughput without}    \\
    backup tasks            & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-4}
    per node                & Backup                                     & Snapshot Store & QFS  \\ \hline
    1                       & 1369.6                                     & 148.0          & 35.3 \\
    2                       & 2408.5                                     & 260.2          & 61.7 \\
    4                       & 4101.8                                     & 443.3          & 103.1 \\
    6                       & 5456.5                                     & 589.7          & 143.8 \\
    \end{tabular}
\caption{Throughput of software layers under different concurrency}
\label{tab:throughput}
\end{table}

{\bf Throughput of software layers.}
Table~\ref{tab:throughput} shows the  average throughput of software layer
when I/O is throttled under 50MB/second and when there is no restriction.
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the gap between this
column and  ``Raw" column is caused by significant data reduction by dirty bit and duplicate
detection. Only non-duplicate chunks trigger a snapshot store write.
``QFS'' column is the write request traffic to the underlying file system after compression.
The underlying disk storage traffic will be three times greater because of replication.
The result shows that the backup service can deliver up to 5.46GB/second without I/O restriction
per machine with 6 concurrent backup tasks. With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.
